### 2016-06-16 Paper_v4.tex
Submission to BioArXiv

Robustness analysis suggested there was no single intervention that inhibited complement activation in the presence of both initiation pathways (Fig. \ref{fig-robustness-analysis}).
Robustness coefficients quantify the response of a protein to a macroscopic structural or operational perturbation to a biochemical network.
Here, we computed how the C3a and C5a trajectories responded to a decrease in the initial abundance of C3 and/or C5 with and without lectin initiator.
We simulated the addition of different doses of anti-complement inhibitor cocktails by decreasing the initial concentration of C3 or C5 or the combination of C3 and C5 by 50\% and 90\%.
This would be conceptually analogous to the administration of a C3 inhibitor e.g., Compstatin alone or combination with Eculizumab (Fig. \ref{fig-SA}C).
A \texttt{log$_{10}$} transformed robustness index of zero indicated no effect due to the perturbation, whereas an index of less than zero indicated decreased C3a or C5a.
The response of the complement model to different knock-down magnitudes was non-linear; a 90\% knock-down had an order of magnitude more impact than a 50\% knock-down.
As expected, a C5 knockdown had no effect on C3a formation for either the alternate (Fig. \ref{fig-robustness-analysis}A, lanes 1 or 3) or lectin pathways
(Fig. \ref{fig-robustness-analysis}B, lanes 1 or 3).
However, C3a abundance and to a lesser extent C5a abundance decreased with decreasing C3 concentration in the alternate pathway (Fig. \ref{fig-robustness-analysis}A or B, lanes 1 or 2).
This agreed with the sensitivity results; changes in AP C3-convertase formation affected the downstream dynamics of C5a formation.
Thus, if we only considered the alternate pathway, C3 alone could be a reasonable target, especially given that C5a formation was surprisingly robust to C5 levels in the alternate pathway (Fig. \ref{fig-robustness-analysis}A or B, lane 2).
Yet, when both pathways were activated, C5a levels were robust to the initial C3 concentration (Fig. \ref{fig-robustness-analysis}A or B, lane 4);
even 10\% of the nominal C3 was able to generated enough C5 convertase to maintain C5a formation.
Thus, the only reliable intervention that consistently reduced both C3a and C5a formation for all cases was a knockdown of both C3 and C5.
For example, a 90\% decrease of both C3 and C5 reduced the formation of C5a by over an order of magnitude (Fig. \ref{fig-robustness-analysis}B, lane 4),
while C3a was reduced to a lesser extent (Fig. \ref{fig-robustness-analysis}B, lane 3).

@@

Robustness coefficients quantify the response of a marker to a structural or operational perturbation to the network architecture.
Robustness coefficients were calculated as shown previously \cite{Tasseff:2011aa}.
Log-transformed robustness coefficients denoted by $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)$ are defined as:
\begin{equation}
\hat{\alpha}\left(i,j,t_{o},t_{f}\right)=\log_{10}\left[\left(\displaystyle\int_{t_{o}}^{t_{f}}x_{i}\left(t\right)dt\right)^{-1}\left(\displaystyle\int_{t_{o}}^{t_{f}}x^{(j)}_{i}\left(t\right)dt\right)\right]
\end{equation}
Here $t_o$ and $t_f$ denote the initial and final simulation time, while $i$ and $j$ denote the indices for the marker and the perturbation, respectively.
A value of $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)>0$, indicates increased marker abundance, while $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)<0$ indicates decreased marker abundance following perturbation $j$. If $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)\sim{0}$, perturbation $j$ did not influence the abundance of marker $i$.
In this study, we perturbed the initial condition of C3 or C5 or a combination of C3 and C5 by 50\% or 90\% and measured the area under the curve (AUC)
of C3a or C5a with and without lectin initiator.
Log-transformed robustness coefficients were calculated for every member of the ensemble, where the mean $\pm$ 1$\times$standard-deviation are reported.

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure5_RobustnessAnalysis_v3.pdf}
\caption{Robustness analysis of the complement model.
Robustness coefficients were calculated for a 50\%, 90\% and 99\% reduction in C3, C5, or C3 and C5 initial conditions.
\textbf{A}: Mean robustness index for C3a and C5a generated from the alternate pathway (w/o zymosan).
\textbf{B}: Mean robustness index for C3a and C5a generated from the lectin and alternate pathway (1 mg/ml zymosan).
The color describes the degree of reduction of C3a or C5a following the network perturbation.
}\label{fig-robustness-analysis}
\end{figure}

>>>>

Robustness analysis suggested there was no single intervention that inhibited complement activation in the presence of both initiation pathways (Fig. \ref{fig-robustness-analysis}).
Robustness coefficients quantify the response of a protein to a macroscopic structural or operational perturbation to a biochemical network.
Here, we computed how the C3a and C5a trajectories responded to a decrease in the initial abundance of C3 and/or C5 with and without lectin initiator.
We simulated the addition of different doses of anti-complement inhibitor cocktails by decreasing the initial concentration of C3, C5 or the combination of C3 and C5 by 50\%, 90\% and 99\%. This would be conceptually analogous to the administration of a C3 inhibitor e.g., Compstatin alone or combination with Eculizumab (Fig. \ref{fig-SA}C).
The response of the complement model to different knock-down magnitudes was non-linear; a 90\% knock-down had an order of magnitude more impact than a 50\% knock-down.
As expected, a C5 knockdown had no effect on C3a formation for either the alternate (Fig. \ref{fig-robustness-analysis}A) or lectin pathways
(Fig. \ref{fig-robustness-analysis}B).
However, C3a and to a greater extent C5a abundance decreased with decreasing C3 concentration in the alternate pathway (Fig. \ref{fig-robustness-analysis}A).
This agreed with the sensitivity results; changes in AP C3-convertase formation affected the downstream dynamics of C5a formation.
Thus, if we only considered the alternate pathway, C3 alone could be a reasonable target, especially given that C5a formation was surprisingly robust to C5 levels in the alternate pathway.
Yet, when both pathways were activated, C5a levels were robust to the initial C3 concentration (Fig. \ref{fig-robustness-analysis}B);
even 1\% of the nominal C3 was able to generated enough AP/CP C5 convertase to maintain C5a formation.
Thus, the only reliable intervention that consistently reduced both C3a and C5a formation for all cases was a knockdown of both C3 and C5.
For example, a 90\% decrease of both C3 and C5 reduced the formation of C5a by an order of magnitude,
while C3a was reduced to a lesser extent (Fig. \ref{fig-robustness-analysis}B).

@@

Robustness coefficients quantify the response of a marker to a structural or operational perturbation to the network architecture.
Robustness coefficients were calculated as shown previously \cite{Tasseff:2011aa}.
Log-transformed robustness coefficients denoted by $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)$ are defined as:
\begin{equation}
\hat{\alpha}\left(i,j,t_{o},t_{f}\right)=\log_{10}\left[\left(\displaystyle\int_{t_{o}}^{t_{f}}x_{i}\left(t\right)dt\right)^{-1}\left(\displaystyle\int_{t_{o}}^{t_{f}}x^{(j)}_{i}\left(t\right)dt\right)\right]
\end{equation}
Here $t_o$ and $t_f$ denote the initial and final simulation time, while $i$ and $j$ denote the indices for the marker and the perturbation, respectively.
A value of $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)>0$, indicates increased marker abundance, while $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)<0$ indicates decreased marker abundance following perturbation $j$. If $\hat{\alpha}\left(i,j,t_{o},t_{f}\right)\sim{0}$, perturbation $j$ did not influence the abundance of marker $i$.
In this study, we perturbed the initial condition of C3 or C5 or a combination of C3 and C5 by 50\%, 90\% and 99\% and measured the area under the curve (AUC)
of C3a or C5a with and without lectin initiator. We computed the robustness coefficients for a subset of the parameter ensemble.

@@

\begin{figure}[h]
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure5_RobustnessAnalysis_v3.pdf}
\caption{Robustness analysis of the complement model.
Robustness coefficients were calculated for a 50\%, 90\% and 99\% reduction in C3, C5, or C3 and C5 initial conditions.
\textbf{A}: Mean robustness index for C3a and C5a generated from the alternate pathway (w/o zymosan).
\textbf{B}: Mean robustness index for C3a and C5a generated from the lectin and alternate pathway (1 mg/ml zymosan).
The color describes the degree of reduction of C3a or C5a following the network perturbation.
Robustness coefficients were calculated using all parameter sets with Pareto rank less than five (N = 65).
}\label{fig-robustness-analysis}
\end{figure}
